\section{Discussion}
\label{sec:discussion}

Guide Dog works well within the limits of what its prototype components were
designed for. However, as a complete system, Guide Dog falls short of the vision
its authors had originally intended for it. It is only able to track brightly
colored objects, it requires that the ground plane be within view at all times,
and it cannot handle the case where the destination object is outside the
viewing range of the camera. 

The most obvious next step for the destination detection component is to replace
it with a more sophisticated, ma\-chine-learning based algorithm that is able to
learn and detect common household objects with high precision.  Such an
algorithm would probably be based on feature learning, such as previous
object-detection work~\cite{lai_icra12}.  This would enable the system to detect
and guide the user to real-world objects of practical interest to the user,
greatly increasing the utility of the system.

An improvement of even greater scope, which would benefit the system as a whole,
would be the addition of a 3D-mapping component and a system for localizing the
camera's position within a pre-existing 3D
map~\cite{Du:2011:IMI:2030112.2030123}. This would allow the system to be placed
into a previously-mapped space, determine its location, and guide the user to a
distant point well outside the line of sight of the camera. A reasonably
sophisticated localization component would remove the need to see the floor at
all times, enabling obstacle detection based on the 3D map, rather than planar
projection. It would also allow shortest paths to be computed through a 3D map,
enabling audio guidance with more detailed cues for guiding the user along the
path (e.g. synthetic speech).

The open source support for RGB-D image processing was impressive. Many of the
``hard'' parts of the project were already implemented. For example, PCL's
planar segmentation worked perfectly to detect the ground plane for obstacle
detection. OpenCV's blob detection was simple to set up and use and was taken
advantage of in both destination and obstacle detection. And OpenAL readily
handled the complexities of 3D sound.

In the future, it would be beneficial to have a fully integrated system
completed earlier. With a fully integrated system it would be easier to test the
audio interface in a real world environment, which would allow for better
iteration and improvement of the audio system.
